Notes

### 2024-10-09 notes.qmd
update: dist with time subsets
feat: add plasma beta statistics
feat: update data
update

---
title: Notes
jupyter: python3
---

@@

@@

-   Analysis
    -   [ ] Re-calculate the occurrence rate of IDs
    -   [ ] Contribution of discontinuities to the power spectrum
    -   [ ] Check Datagap
    -   [ ] Check `ARTEMIS-B` data in different states (solar wind, magnetosheath, magnetotail, moon wake)
    -   [ ] Distribution of \|B\| over radius
    -   [ ] JUNO from 2012-09\~2012-10 lack of IDS and extreme large thickness
    -   [ ] Wind data
    -   [ ] Add error bar
    -   [ ] Validate the effects of calibrate candidate duration
    -   [ ] Validate model density with `Voyager`
-   Identifaction
    -   [ ] Ensemble forest?
    -   [ ] Smoothing is important?
    -   [ ] Check change point algorithm
-   Visualize data gaps
-   Features
    -   [ ] Thickness in N direction
    -   [ ] Use high resolution data for feature extraction
-   Compare with other methods of identifying IDs
    -   [ ] Verify with other methods of identifying IDs
-   [x] Incorporate solar wind propagation model
    -   [x] Verify with solar wind propagation model
        -   [x] Coordinate transformation

>>>>

---
title: Notes
---

# Data

`updated_events_JNO_method=fit_tau=0:01:00_ts=0:00:01.arrow` and `events.JNO.fit.ts_1.00s_tau_60s.arrow` are the same data for backward compatibility.

`updated_events_Wind_tr=20110825-20160630_method=fit_tau=0:01:00_ts=0:00:00.090909.arrow` and `events.Wind.fit.ts_0.09s_tau_60s.arrow`

@@

### 09/23/2024

::: {.column-page}
::: {#fig-ocr-v layout-nrow="1"}

![Wind](figures/ocr/ocr_wind_daily_v.svg)

![](images/söding2001_fig4.png)

Distribution of daily averages of DD per day over v with the fit of an linear function.
:::
:::

@@

-   Analysis
    -   [ ] Re-calculate the occurrence rate of IDs
    -   [x] Distribution of $δB/B$ over radius (related to the alfvenicity, identification standard about neighboring fluctuations)
    -   [x] $\theta_{n,v}$ distribution
    -   [ ] Correlation between plasma beta and thickness / current density

    -   [ ] Check Datagap
    -   [ ] Check `ARTEMIS-B` data in different states (solar wind, magnetosheath, magnetotail, moon wake)
    -   [ ] Distribution of \|B\| over radius
    -   [ ] JUNO from 2012-09\~2012-10 lack of IDS and extreme large thickness
    -   [ ] Wind data
    -   [ ] Add error bar
    -   [ ] Validate the effects of calibrate candidate duration

    -   ~~Contribution of discontinuities to the power spectrum~~
    -   ~~Validate model density with `Voyager`~~
-   Identifaction
    -   [ ] Ensemble forest?
    -   [ ] Smoothing is important?
    -   [ ] Check change point algorithm
-   Visualize data gaps
-   Features
    -   [ ] Thickness in N direction
    -   [ ] Use high resolution data for feature extraction
-   Compare with other methods of identifying IDs
    -   [ ] Verify with other methods of identifying IDs
-   [x] Incorporate solar wind propagation model
    -   [x] Verify with solar wind propagation model
        -   [x] Coordinate transformation
